Baseline centering problem

### 2018-11-24 paper/tangotd.tex

If we parameterize $V$ by some parameter $\theta$, we can apply
parametric TD. The expected TD step is
\begin{equation}
\theta\gets \theta -\eta \,\transp{\Phi}\rho (V-PV-R)
\end{equation}
where 
\begin{equation}
\Phi\deq \frac{\partial V}{\partial \theta}
\end{equation}
is the Jacobian matrix of $V$ with respect to its parameter. The linear
case $V=\Phi \theta$ corresponds to constant $\Phi$.

@@

In particular, a symmetric, definite positive matrix is stable. Since the
solution of $\theta_t'=-A\theta_t$ is $\theta_t=e^{-tA}\theta_0$, a
Lyapunov function that works is $\transp{\theta}L\theta=\int_{t \geq 0}
\norm{\theta_t}^2$, namely
$L=\int_{t\geq 0} \transp{(e^{-t A})}
e^{-tA}$.

>>>>

If we parameterize $V$ by some parameter $\theta$, we can apply
parametric TD. The expected TD step is
\begin{equation}
\theta\gets \theta -\eta \,\transp{\Phi}\rho (V-PV-R)
\end{equation}
where 
\begin{equation}
\Phi\deq \frac{\partial V}{\partial \theta}
\end{equation}
is the Jacobian matrix of $V$ with respect to its parameter. The linear
case $V=\Phi \theta$ corresponds to constant $\Phi$. The tabular case is
$\Phi=\Id$.

@@

In particular, a symmetric, definite positive matrix is stable (last
criterion with $L=\Id$).
Stability is invariant by matrix similarity $A\gets B^{-1}A B$, since
this preserves eigenvalues.

Since the
solution of $\theta_t'=-A\theta_t$ is $\theta_t=e^{-tA}\theta_0$, a
Lyapunov function that works is $\transp{\theta}L\theta=\int_{t \geq 0}
\norm{\theta_t}^2$, namely
$L=\int_{t\geq 0} \transp{(e^{-t A})}
e^{-tA}$.

\paragraph{Making the TD iteration stable.} In linear TD the matrix $A$ is
\begin{equation}
A=\transp{\Phi}\rho (\Id-P)\Phi
\end{equation}
and we know it is stable in several cases: (TODO here I just remove
constants)
\begin{enumerate}
\item On-policy: $\rho=\mu$, the invariant distribution. Then we know that $\rho(\Id-P)$ is positive
(Dirichlet form). This implies that $\transp{\Phi}\rho (\Id-P)\Phi$ is
positive too. So we recover the convergence result on-policy for linear
TD.
\item In the tabular case: $\Phi=\Id$. Indeed we have $A=\rho (\Id-P)$,
which is not positive in general, but since $\mu (\Id-P)$ is, we can take
$L=\mu/\rho$ so that $LA$ is positive.
\end{enumerate}

One can also \emph{precondition} the gradient descent. This can make it
stable and/or make convergence faster. The step becomes
\begin{equation}
\theta\gets \theta-\eta B(A\theta-b)
\end{equation}
for some matrix $B$.

Of course the values of $B$ that are most interesting are obtained as the
inverse of something; for instance $B=A^{-1}$ solves the problem
instantly... Two-timescale methods or TANGO-like algorithms can apply an
inverse of something to $A\theta-b$, via an auxiliary gradient descent.
TANGO works for stable matrices, if they are samplable \footnote{In
TANGO, the consecutive steps absolutely have to be \emph{independent}. So even in
the on-policy case, we will need a replay buffer from $\mu$ for the auxiliary
gradient descent.}

A few choices are:
\begin{itemize}
\item $B=A^{-1}$: obviously stable, jumps to the solution in one step if
$\eta=1$. Requires computing the inverse of $A$, namely, solving the
problem.
\end{itemize}
